On Designing Collusion-Resistant Incentive Mechanisms for Mobile Crowdsensing Systems

### 2015-12-10 techreport.tex
Make the strategyproof property of the discrete game EXPLICITLY.
Actually this revision corresponds to Reviewer 1's Comment 1:
``
So, it is better to give a lemma or a theorem =
to explicitly prove that the proposed mechanism is strategyproof. =
Actually, only Lemma 3 in this paper is related to this issue. =
Nevertheless, this Lemma still has not shown the strategyproof property =
explicitly.
''

Now we can show our main results:
\begin{figure}[!t]
\centering{}
\setlength{\unitlength}{1cm}
\begin{picture}(4,4)(-1.5,-0.5)
\put (-4,1){\vector(1,0){4.2}}% draw x axe
\put (-3,0){\vector(0,1){3.2}} %draw y axe
\qbezier(-1.2,1.6)(-2.15,1.6)(-2.4,-0.2)% draw graph
\qbezier(-1.2,1.6)(-0.25,1.6)(0,-0.2)
\put(-1.2,0){\line(0,1){3.2}} % draw solid lines
\multiput(-2,0)(0,0.2){16}{\line(0,1){0.1}}	% draw dashed lines
\multiput(-1,0)(0,0.2){16}{\line(0,1){0.1}}
\multiput(0,0)(0,0.2){16}{\line(0,1){0.1}}
\put (-1.4,0.6){$\hat{x}$}
\put (-1.0,1){\circle{0.1}}
\put (-0.95,0.6){$\lfloor \hat{x}+\frac{1}{2}\rfloor$}
\put (-2,-0.5){(a)}% lengend

@@

\begin{lemma}
\label{lem:quadratic}
The nonnegative integer $n_i$ that maximizes the user utility $u_i = p_i - \kappa_in_i$ is $\max_{i\in U} \{m-\lfloor \kappa_i/d \rfloor, 0\}$.
\end{lemma}
\begin{IEEEproof}
In fact the utility may be real-extended into a concave quadratic function as follows:
\[ u_i(n_i) = p_i - \kappa_in_i = \frac{1}{2}n_i(2m+1-n_i)d - \kappa_in_i. \]
Its function graph is a parabola with the axis of symmetry $\hat{x}=m-\frac{\kappa_i}{d}+\frac{1}{2}$. It is easy to verify that the integer closest to the axis of symmetry can obtain the maximum utility. Figure \ref{fig:quad_prop} gives the two possible cases of the axis position. For both cases $m-\lfloor \kappa_i/d \rfloor$ is the integer closest to the symmetric axis.\footnote{It is possible that the axis satisfies both the cases. Then it has two nearest integers and we can choose either of them.} If the closest integer is nonnegative, we get the desired $n_i$ immediately. If the closest integer is negative, then the axis of symmetry must reside to the left of the $y$ axis. Hence the utility function monotonically decreases over $[0,+\infty)$. As a result the nonnegative integer $n_i$ that maximizes $u_i$ must be 0. Both cases give the lemma.
\end{IEEEproof}

\begin{theorem}
\label{thm:discrete}
For any discrete crowdsensing game with user utility equation $u_i = p_i - \kappa_in_i$, the incentive mechanism given by Algorithm \ref{alg:np} can achieve group strategyproof and n-truthful equilibrium.
\end{theorem}
\begin{IEEEproof}
Clearly the utility of each user $i$ is not parametric dependent on any other user strategy. We may view $n_i$ as restricting the $t_i$ in (\ref{eqn:user_utility_2}) onto integers. %Then the statements in Theorem \ref{thm:main} and Theorem \ref{thm:pt} still hold for the case $u_i = p_i - \kappa_in_i$. 
Theorem \ref{thm:main} guarantees that to complete this proof, it suffices to show that the incentive mechanism given by Algorithm \ref{alg:np} can achieve strategyproof equilibrium. For any user $i$, to maximize its utility $u_i = p_i - \kappa_in_i$, $n_i$ must be $\max_{i\in U}\{m-\lfloor \kappa_i/d \rfloor, 0\}$ by Lemma \ref{lem:quadratic}. In other words, there will be no gain if user $i$ makes its strategy $s_i$ different from the true cost unit $\kappa_i$. This fact implies the strategyproof equilibrium.
\end{IEEEproof}
}
{\color{black}Note that there will be no gain or loss if user $i$ selects any other points within the ($m+1-n_i$)-th interval. Thus a small partition interval is beneficial to the truthful mechanism, since each user has less freedom to perturb the truthful strategy.}

@@

\bibliographystyle{./IEEEtran}
\bibliography{./13fall_1ed}
\pagebreak

>>>>

{\color{blue} Before we introduce our main results, we need Lemma \ref{lem:quadratic}, which gives the strategyproof equilibrium for the discrete crowdsensing game. }
\begin{figure}[!t]
\centering{}
\setlength{\unitlength}{1cm}
\begin{picture}(4,4)(-1.5,-0.5)
\put (-4,1){\vector(1,0){4.2}}% draw x axe
\put (-3,0){\vector(0,1){3.2}} %draw y axe
\qbezier(-1.2,1.6)(-2.15,1.6)(-2.4,-0.2)% draw graph
\qbezier(-1.2,1.6)(-0.25,1.6)(0,-0.2)
\put(-1.2,0){\line(0,1){3.2}} % draw solid lines
\multiput(-2,0)(0,0.2){16}{\line(0,1){0.1}}	% draw dashed lines
\multiput(-1,0)(0,0.2){16}{\line(0,1){0.1}}
\multiput(0,0)(0,0.2){16}{\line(0,1){0.1}}
\put (-1.4,0.6){$\hat{x}$}
\put (-1.0,1){\circle{0.1}}
\put (-0.95,0.6){$\lfloor \hat{x}+\frac{1}{2}\rfloor$}
\put (-2,-0.5){(a)}% lengend

@@

\begin{lemma}
\label{lem:quadratic}
The nonnegative integer $n_i$ that maximizes the user utility $u_i = p_i - \kappa_in_i$ is $\max_{i\in U} \{m-\lfloor \kappa_i/d \rfloor, 0\}$.
{\color{blue} That is, if any $n_i = \max_{i\in U} \{m-\lfloor \kappa_i/d \rfloor, 0\}$, then the discrete crowdsensing game achieves strategyproof equilibrium. }
\end{lemma}
\begin{IEEEproof}
In fact the utility may be real-extended into a concave quadratic function as follows:
\[ u_i(n_i) = p_i - \kappa_in_i = \frac{1}{2}n_i(2m+1-n_i)d - \kappa_in_i. \]
Its function graph is a parabola with the axis of symmetry $\hat{x}=m-\frac{\kappa_i}{d}+\frac{1}{2}$. It is easy to verify that the integer closest to the axis of symmetry can obtain the maximum utility. Figure \ref{fig:quad_prop} gives the two possible cases of the axis position. For both cases $m-\lfloor \kappa_i/d \rfloor$ is the integer closest to the symmetric axis.\footnote{It is possible that the axis satisfies both the cases. Then it has two nearest integers and we can choose either of them.} If the closest integer is nonnegative, we get the desired $n_i$ immediately. If the closest integer is negative, then the axis of symmetry must reside to the left of the $y$ axis. Hence the utility function monotonically decreases over $[0,+\infty)$. As a result the nonnegative integer $n_i$ that maximizes $u_i$ must be 0. Both cases give the lemma.
\end{IEEEproof}

Now we can show our main results, Theorem \ref{thm:discrete}.
\begin{theorem}
\label{thm:discrete}
For any discrete crowdsensing game with user utility equation $u_i = p_i - \kappa_in_i$, the incentive mechanism given by Algorithm \ref{alg:np} can achieve group strategyproof and n-truthful equilibrium.
\end{theorem}
\begin{IEEEproof}
Clearly the utility of each user $i$ is not parametric dependent on any other user strategy. We may view $n_i$ as restricting the $t_i$ in (\ref{eqn:user_utility_2}) onto integers. %Then the statements in Theorem \ref{thm:main} and Theorem \ref{thm:pt} still hold for the case $u_i = p_i - \kappa_in_i$. 
Theorem \ref{thm:main} guarantees that to complete this proof, it suffices to show that the incentive mechanism given by Algorithm \ref{alg:np} can achieve strategyproof equilibrium. For any user $i$, to maximize its utility $u_i = p_i - \kappa_in_i$, $n_i$ must be $\max_{i\in U}\{m-\lfloor \kappa_i/d \rfloor, 0\}$ by Lemma \ref{lem:quadratic}. In other words, there will be no gain if user $i$ makes its strategy $s_i$ different from the true cost unit $\kappa_i$. This fact implies the strategyproof equilibrium.
\end{IEEEproof}
}
{\color{black}Note that there will be no gain or loss if user $i$ selects any other points within the ($m+1-n_i$)-th interval. Thus a small partition interval is beneficial to the truthful mechanism, since each user has less freedom to perturb the truthful strategy.}

@@

\bibliographystyle{./IEEEtran}
\bibliography{./13fall_1ed}
%\pagebreak
